\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-08 response.tex

\begin{document}

\newtcbtheorem[auto counter, number within = section]{cmt}{Comment}{
	colbacktitle = black!60!white, colframe = black!60!white,
	colback = black!5!white,
	fonttitle=\bfseries,%fontupper=\itshape,
}{t}

\noindent
Dear Editor and Reviewers:

\vspace{0.2cm}
\noindent
First and foremost, we sincerely thank the Editor-in-Chief, Associate Editor, and anonymous reviewers for their insightful comments and suggestions. These have been carefully incorporated into the revised manuscript, resulting in a clearer, more informative, and more readable version. We acknowledge the reviewers' concerns regarding grammatical errors, unclear definitions, and poorly formatted figures, which were noted as obstacles to evaluating the paper's technical contributions. In this revision, we have thoroughly addressed these issues by eliminating grammatical errors, refining definitions and notations for clarity, and replotting the figures to enhance readability. All reviewer comments have been carefully addressed, and the corresponding changes have been highlighted in \new{blue} for ease of reference. Our detailed responses to the reviewers' comments, provided in a 1:1 correspondence, are outlined below.
\vspace{0.2cm}
\noindent
Yours sincerely,

### 2024-12-08 paper.tex
Finish refinine paper, working on response

A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}. Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accommodate for more flexible objectives. In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.

@@

\begin{figure}
  \centering
  \subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.47\linewidth, trim = 2cm 1cm 1cm 1cm,clip,valign=b]{old_result_v2}}
  \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
  \caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as dotted arrows on top of the original plan in \cref{fig:previous_result_plan}. (\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}
  \label{fig:3-team-ctco}
\end{figure}

>>>>

A preliminary version of the paper is presented in \cite{yang2020multi,yang2021multi}. Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accommodate for more flexible objectives. In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.

@@

\begin{figure}
  \centering
  \subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.47\linewidth, trim = 2cm 1cm 1cm 1cm,clip,valign=b]{old_result_v2}}
  \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
  \caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as arrows on top of the original plan in \cref{fig:previous_result_plan}. (\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}
  \label{fig:3-team-ctco}
\end{figure}
